Staged Abstract Interpreters

### 2019-09-11 paper/50_stageabs.tex
polish

We have implemented a big-step, compositional abstract interpreter in monadic
style, where \textit{compositional} means that every recursive call of our abstract
interpreter is applied to the proper substructures of the current syntactic
parameters \cite{10.1007/3-540-61580-6_11}. This compositionality ensures that
specialization can be done by unfolding, as well as guarantees the termination
of the specialization procedure. It is also possible to specialize a small-step
operational abstract semantics through abstract compilation
\cite{Boucher:1996:ACN:647473.727587} -- as
\citet{Johnson:2013:OAA:2500365.2500604} presented for
optimizing Abstract Abstract Machines. However, the generated abstract
bytecode still requires another small-step abstract machine to execute, which is
an additional engineering effort.

>>>>

We have implemented a big-step, compositional abstract interpreter in monadic
style, where \textit{compositional} means that every recursive call of @eval@ %our abstract
is applied to the proper substructures of the current syntactic
parameters \cite{10.1007/3-540-61580-6_11}. This compositionality ensures that
specialization can be done by unfolding, as well as guarantees the termination
of the specialization procedure. It is also possible to specialize a small-step
operational abstract semantics through abstract compilation
\cite{Boucher:1996:ACN:647473.727587} -- as
\citet{Johnson:2013:OAA:2500365.2500604} presented for
optimizing Abstract Abstract Machines. However, the generated abstract
bytecode still requires another small-step abstract machine to execute, which is
an additional engineering effort.

### 2019-09-11 paper/paper.tex
polish

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  We thank the reviewers of PLDI '19 and OOPSLA '19, as well as James Decker,
  Guanhong Tao, Gr\'egory Essertel, and Fei Wang for their feedback on the early
  drafts. We thank David Van Horn and David Darais for their encouragement on
  this work.
  This work was supported in part by NSF awards 1553471, 1564207, 1918483, DOE
  award DE-SC0018050, as well as gifts from Google, Facebook, and VMware.

>>>>

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  We thank the reviewers of PLDI '19 and OOPSLA '19, as well as James Decker,
  Guanhong Tao, Gr\'egory Essertel, Fei Wang, Qianchuan Ye, and Yapeng Ye for
  their feedback on the early drafts. We thank David Van Horn and David Darais
  for their encouragement on this work.
  This work was supported in part by NSF awards 1553471, 1564207, 1918483, DOE
  award DE-SC0018050, as well as gifts from Google, Facebook, and VMware.
